---
title: "Assignment_new_new"
author: "Islam Islamov(444601)"
date: today
output: html_document
params:
  data: "../Quarto and MD 3/Data/season_1.csv"
  season: 1

---

```{r}
setwd("C:/Users/isisl/OneDrive/Desktop/RRcourse2023/Quarto and MD 3")
season_data <- read.csv(params$data)
```

# Game of Thrones - Season `r params$season` summary in numbers

### Season `r params$season` summary

> Season `r params$season` of Game of Thrones consisted of `r nrow(season_data)` episodes that aired between `r season_data$premiere_date[1]` and `r season_data$premiere_date[nrow(season_data)]` on HBO. The show gathered an average of `r mean(season_data$viewers)` first-day TV viewers in the US, with the number growing from `r season_data$viewers[1]` to `r season_data$viewers[nrow(season_data)]` million by the end of the season.


You can see how the viewership of the episodes changed in Figure 1.

```{r}
#| label = "viewers_plot"
plot(season_data$viewers, type="l", col="red", lwd=5, xlab = "Episode number", ylab = "1st day TV viewers in the US (millions)")
```

***

You can see the average viewership for the season

```{r, results='asis', echo = FALSE}
avg_viewership <- mean(season_data$viewers)
avg_viewership
```

Finally, the episodes with the above-average viewership were:
```{r, echo = FALSE }

filtered_data <- season_data[season_data$viewers <= avg_viewership, c("no_season", "viewers")]

# Create a list of seasons and viewership values
chart <- paste(filtered_data$no_season, "-", filtered_data$viewers)

# Display the chart
chart


```